---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# dndselectr

[![Travis-CI Build Status](https://travis-ci.org/serenity-r/dndselectr.svg?branch=master)](https://travis-ci.org/serenity-r/dndselectr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/serenity-r/dndselectr?branch=master&svg=true)](https://ci.appveyor.com/project/mdlama/dndselectr)
[![Coverage Status](https://img.shields.io/codecov/c/github/serenity-r/dndselectr/master.svg)](https://codecov.io/github/serenity-r/dndselectr?branch=master)
[![Lifecycle Experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

## Overview

Implements a drag-and-drop Shiny select input

This implementation creates a Shiny input that replicates much of the functionality of selectInput. 
Multiple zones for dragging and dropping are allowed.
Currently utilizes Dragula JS library, https://github.com/bevacqua/dragula.

## Installation

```{r, eval = FALSE}
# Install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("serenity-r/dndselectr")
```

## Examples

```{r}
dndselectr::runExample()
```

Please note that the 'dndselectr' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
